---
title: "Covid-19 Data Visualization Dashboard of India"

output:
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill



    
---


```{r setup, include=FALSE}
#importing libraries
library(flexdashboard)
library(knitr)
library(rpivotTable)
library(ggplot2)
library(plotly)
library(dplyr)
library(openintro)
library(DT)
library(viridis)
library(gt)
library(tidyverse)
library(highcharter)
library(hrbrthemes)
library(htmltools)
library(htmltools)
library(sf)
library(rvest)
library(ggrepel)
library(ggthemes)
library(geojsonio)


```


```{r}
# cleaning the data as the data is in a comma formatted numbers and hence we need to convert it into a number format so # # that we can make graphs and do calculations with it

df <-  read.csv("indiadata.csv", header=T)


df <- df %>%
  mutate(across(c(Totalcases, Discharged, Deaths, Population, Vaccination,
                  Doseone, Dosetwo, Doseone1518, Dosetwo1518, Doseone1214, Dosetwo1214,Precaution1859,Precaution),
                ~ as.numeric(gsub(",", "", .))))



# Convert Date column to Date format (if not already)







```








Overview
===============================================


Column {data-width=50}
--------------------------------------------------------------------------

### COVID-19 Cases in India
```{r}
valueBox("45,001,456", icon = "fa-rupee-sign", color= "#FFA500")
```

### Deaths in India  due to COVID-19
```{r}
valueBox("533,295", icon = "fa-rupee-sign", color= "#960018")

```

### People recovered in India
```{r}
valueBox("44,481,893", icon = "fa-rupee-sign", color= "#00308F")

```

### Total COVID-19 vaccine doses administered in India
```{r}
valueBox("2.21 bn", icon = "fa-rupee-sign", color= "#FFFDD0")
```

### Percentage of Population Vaccinated 
```{r}
valueBox("69%", icon = "fa-rupee-sign", color= "#023020")
```


Column{.tabset .tabset-fade data-width=550}
------------------------------------------------------------------------

### Cases



```{r}

# Load data and format Date column
df <- read.csv("who.csv", header = TRUE)
df$Date <- as.Date(df$Date, format = "%d/%m/%Y")

# Create the highchart object for Cases over Time
highchart() %>%
  hc_chart(
    type = "line"  # Set chart type to line
  ) %>%
  hc_title(text = "Cases Over Time")%>%  # Set chart title
  hc_xAxis(categories = df$Date)%>%  # Set x-axis categories to Date column
  hc_yAxis(title = list(text = "No of Cases"))%>%  # Set y-axis title
  hc_series(list(name = "Cases", data = df$New_cases_ind))%>%  # Add series for Cases data
  hc_exporting(
    enabled = TRUE  # Enable exporting functionality
  ) %>%
  hc_credits(
    enabled = TRUE,
    text = "WHO",  # Credits to WHO
    href = "https://data.who.int/dashboards/covid19/cases?m49=356&n=c"  # WHO data source
  )



```

### Deaths
```{r}
# Load data and format Date column
df <-  read.csv("who.csv", header=T)
df$Date <- as.Date(df$Date,format = "%d/%m/%Y")

# Create the highchart object for Deaths over Time
highchart() %>%
  hc_chart(type = "line") %>%
  hc_title(text = " Deaths Over Time") %>%
  hc_xAxis(categories = df$Date) %>%
  hc_yAxis(title = list(text = "No of Deaths")) %>%
  hc_series(list(name = "Deaths", data = df$New_deaths_ind)) %>%
  hc_exporting(
    enabled = TRUE  # Enable exporting functionality
  ) %>%
  hc_credits(
    enabled = TRUE,
    text = "WHO",  # Credits to WHO
    href = "https://data.who.int/dashboards/covid19/cases?m49=356&n=c"  # WHO data source
  )




```

Column{data-width=400}
------------------------------------


### Cumulative Cases in India
    
```{r}
# Load data and format Date column
df <-  read.csv("who.csv", header=T)
df$Date <- as.Date(df$Date,format = "%d/%m/%Y")

# Create the highchart object for Cumulative Cases over Time
highchart() %>%
  hc_chart(type = "line") %>%
  hc_title(text = "Cumulative Cases Over Time") %>%
  hc_xAxis(categories = df$Date) %>%
  hc_yAxis(title = list(text = "Cumulative Cases")) %>%
  hc_series(list(name = "Cumulative Cases", data = df$Cumulative_cases)) %>%
  hc_exporting(
    enabled = TRUE  # Enable exporting functionality
  ) %>%
  hc_credits(
    enabled = TRUE,
    text = "WHO",  # Credits to WHO
    href = "https://data.who.int/dashboards/covid19/cases?m49=356&n=c"  # WHO data source
  )

```
    
### Cumulative Deaths in India

```{r}

# Load data and format Date column
df <-  read.csv("who.csv", header=T)
df$Date <- as.Date(df$Date,format = "%d/%m/%Y")

# Create the highchart object for Cumulative Deaths over Time
highchart() %>%
  hc_chart(type = "line") %>%
  hc_title(text = "Cumulative Deaths Over Time") %>%
  hc_xAxis(categories = df$Date) %>%
  hc_yAxis(title = list(text = "Cumulative Deaths")) %>%
  hc_series(list(name = "Cumulative Deaths", data = df$Cumulative_deaths)) %>%
  hc_exporting(
    enabled = TRUE  # Enable exporting functionality
  ) %>%
  hc_credits(
    enabled = TRUE,
    text = "WHO",  # Credits to WHO
    href = "https://data.who.int/dashboards/covid19/cases?m49=356&n=c"  # WHO data source
  )

```


Statewise Visualisation
=====================================================

Column {.tabset .tabset-fade data-width=400}
--------------------------------------------------
    
### Cases 
    
```{r}
# Load the data
df <- read.csv("indiadata.csv", header=T)

# Convert certain columns to numeric by removing commas
df <- df %>%
  mutate(across(c(Totalcases, Discharged, Deaths, Population, Vaccination,
                  Doseone, Dosetwo, Doseone1518, Dosetwo1518, Doseone1214, Dosetwo1214, Precaution1859, Precaution),
                ~ as.numeric(gsub(",", "", .))))

# Reshape dataframe from wide to long format
df_long <- pivot_longer(df, cols = c(Totalcases, Discharged), names_to = "Category", values_to = "Value")

# Create a bar chart using highcharter
hchart(df_long, "bar", hcaes(x = State, y = Value, group = Category)) %>%
  hc_title(text = "Comparison of Cases and Recovery By States") %>%
  hc_subtitle(text = "Grouped Column Chart") %>%
  hc_xAxis(title = list(text = "State")) %>%
  hc_yAxis(title = list(text = "Comparison of Cases and Recovery ")) %>%
  hc_legend(enabled = TRUE) %>%
  hc_colors(c("Totalcases" = "red", "Discharged" = "blue"))%>%  # Specify custom colors for Totalcases and Discharged bars
  hc_chart(zoomType = "xy")%>%  # Enable zooming functionality
  hc_exporting(
    enabled = TRUE  # Enable exporting functionality
  ) %>%
  hc_credits(
    enabled = TRUE,
    text = "ndtv",  # Credits to ndtv
    href = "https://www.ndtv.com/coronavirus/india-covid-19-tracker"  # Link to ndtv source
  )





```



### Deaths

```{r}
# Read the dataset
df <- read.csv("indiadata.csv", header = TRUE)

# Convert character columns with commas to numeric
df <- df %>%
  mutate(across(c(Totalcases, Discharged, Deaths, Population, Vaccination,
                  Doseone, Dosetwo, Doseone1518, Dosetwo1518, Doseone1214, Dosetwo1214, Precaution1859, Precaution),
                ~ as.numeric(gsub(",", "", .))))

# Sort the dataframe by Deaths column in descending order
df <- df %>%
  arrange(desc(Deaths))

# Create a pie chart using highcharter
highchart() %>%
  hc_chart(type = "pie") %>%
  hc_title(text = "Pie Chart of Deaths by State") %>%
  hc_add_series(data = list_parse2(df[, c("State", "Deaths")])) %>%
  hc_tooltip(
    pointFormat = "<b>{point.name}:</b> {point.y} Deaths"  # Specify tooltip format
  ) %>%
  hc_exporting(
    enabled = TRUE  # Enable exporting functionality
  ) %>%
  hc_credits(
    enabled = TRUE,
    text = "ndtv",  # Credits to ndtv
    href = "https://www.ndtv.com/coronavirus/india-covid-19-tracker"  # Link to ndtv source
  )



```

### PofCases

```{r}
# Read the dataset
df <- read.csv("indiadata.csv", header = TRUE)

# Convert character columns with commas to numeric
# Calculate Cases per Capita and round to 2 decimal places
df <- df %>%
  mutate(across(c(Totalcases, Discharged, Deaths, Population, Vaccination,
                  Doseone, Dosetwo, Doseone1518, Dosetwo1518, Doseone1214, Dosetwo1214, Precaution1859, Precaution),
                ~ as.numeric(gsub(",", "", .))),
         Cases_Per_Capita = round(Totalcases / Population, 2)
  )

# Create a treemap
hchart(df, "treemap", hcaes(x = State, value = Cases_Per_Capita, color = Cases_Per_Capita)) %>%
  hc_title(text = "Probability of State affected by COVID-19") %>%
  hc_subtitle(text = "Treemap") %>%
  hc_colorAxis(minColor = "#FFFFFF", maxColor = "skyblue") %>%  # Customize color axis
  hc_exporting(
    enabled = TRUE  # Enable exporting functionality
  ) %>%
  hc_credits(
    enabled = TRUE,
    text = "mygov.in",  # Credits to mygov.in
    href = "https://www.mygov.in/covid-19/"  # Link to mygov.in source
  )


```


### PofDeath

```{r}
# Read the dataset
df <- read.csv("indiadata.csv", header = TRUE)

# Convert character columns with commas to numeric
# Calculate Cases per Capita and round to 5 decimal places
df <- df %>%
  mutate(across(c(Totalcases, Discharged, Deaths, Population, Vaccination,
                  Doseone, Dosetwo, Doseone1518, Dosetwo1518, Doseone1214, Dosetwo1214, Precaution1859, Precaution),
                ~ as.numeric(gsub(",", "", .))),
         Cases_Per_Capita = round(Deaths / Population, 5)
  )

# Create a treemap
hchart(df, "treemap", hcaes(x = State, value = Cases_Per_Capita, color = Cases_Per_Capita)) %>%
  hc_title(text = "Probability of State deaths by COVID-19") %>%
  hc_subtitle(text = "Treemap") %>%
  hc_colorAxis(minColor = "#FFFFFF", maxColor = "red") %>%  # Customize color axis
  hc_exporting(
    enabled = TRUE  # Enable exporting functionality
  ) %>%
  hc_credits(
    enabled = TRUE,
    text = "mygov.in",  # Credits to mygov.in
    href = "https://www.mygov.in/covid-19/"  # Link to mygov.in source
  )

```

### PofRecovery

```{r}
# Read the dataset
df <- read.csv("indiadata.csv", header = TRUE)

# Convert character columns with commas to numeric
# Calculate Cases per Capita (Recovered) and round to 5 decimal places
df <- df %>%
  mutate(across(c(Totalcases, Discharged, Deaths, Population, Vaccination,
                  Doseone, Dosetwo, Doseone1518, Dosetwo1518, Doseone1214, Dosetwo1214, Precaution1859, Precaution),
                ~ as.numeric(gsub(",", "", .))),
         Cases_Per_Capita = round(Discharged / Population, 5)
  )

# Create a treemap
hchart(df, "treemap", hcaes(x = State, value = Cases_Per_Capita, color = Cases_Per_Capita)) %>%
  hc_title(text = "Probability of State Recovered by COVID-19") %>%
  hc_subtitle(text = "Treemap") %>%
  hc_colorAxis(minColor = "#FFFFFF", maxColor = "lightgreen") %>%  # Customize color axis
  hc_exporting(
    enabled = TRUE  # Enable exporting functionality
  ) %>%
  hc_credits(
    enabled = TRUE,
    text = "mygov.in",  # Credits to mygov.in
    href = "https://www.mygov.in/covid-19/"  # Link to mygov.in source
  )

```



Column{data-width= 200}
-------------------------------------

### Vaccination

```{r}
# Read the dataset
df <- read.csv("indiadata.csv", header = TRUE)

# Convert character columns with commas to numeric
df <- df %>%
  mutate(across(c(Totalcases, Discharged, Deaths, Population, Vaccination,
                  Doseone, Dosetwo, Doseone1518, Dosetwo1518, Doseone1214, Dosetwo1214, Precaution1859, Precaution),
                ~ as.numeric(gsub(",", "", .))))

# Create a treemap
hchart(df, "treemap", hcaes(x = State, value = Vaccination, color = Vaccination)) %>%
  hc_title(text = "Vaccinations by State") %>%
  hc_subtitle(text = "Treemap") %>%
  hc_colorAxis(minColor = "#FFFFFF", maxColor = "darkgreen") %>%  # Customize color axis
  hc_exporting(
    enabled = TRUE  # Enable exporting functionality
  ) %>%
  hc_credits(
    enabled = TRUE,
    text = "mygov.in",  # Credits to mygov.in
    href = "https://www.mygov.in/covid-19/"  # Link to mygov.in source
  )


```



### Statewise Recovery 

```{r}
# Read the dataset
df <- read.csv("indiadata.csv", header = TRUE)

# Calculate mean of discharge ratio and death ratio
a <- mean(df$Discharge.Ratio) * 100
b <- mean(df$Deathratio) * 100

# Define custom colors for the pie chart
custom_colors <- viridis::plasma(n = 2)

# Create a dataframe with labels and proportions
df <- data.frame(Label = c("Recovery Ratio", "Death Ratio"),
                 Proportion = c(98.89, 1.11))

# Create a pie chart
df %>%
  hchart(type = "pie", hcaes(x = Label, y = Proportion, color = custom_colors)) %>%
  
  # Add Google theme
  hc_add_theme(hc_theme_google()) %>%
  
  # Set chart title and subtitle
  hc_title(text = "Effect of Covid 19 on the Indian Population") %>%
  hc_subtitle(text = "Proportions in Percentage") %>%
  
  # Define tooltip format
  hc_tooltip(pointFormat = "<b>{point.name}:</b> {point.percentage:.2f}%") %>%
  
  # Enable legend
  hc_legend(enabled = TRUE) %>%
  
  # Enable exporting functionality
  hc_exporting(
    enabled = TRUE
  ) %>%
  
  # Add credits
  hc_credits(
    enabled = TRUE,
    text = "mygov.in",  # Credits to mygov.in
    href = "https://www.mygov.in/covid-19/"  # Link to mygov.in source
  )

```

Column{.tabset .tabset-fade data-width=400}
--------------------------------------------------------------

### Vaccinations by Top 20 States

```{r}

# Read the dataset
df <- read.csv("indiadata.csv", header = TRUE)

# Convert character columns with commas to numeric
df <- df %>%
  mutate(across(c(Totalcases, Discharged, Deaths, Population, Vaccination,
                  Doseone, Dosetwo, Doseone1518, Dosetwo1518, Doseone1214, Dosetwo1214, Precaution1859, Precaution),
                ~ as.numeric(gsub(",", "", .))))

# Sort the dataframe by Vaccination column in descending order and select top 20 rows
df <- df %>% 
  arrange(desc(Vaccination)) %>%
  head(20)

# Reshape dataframe from wide to long format
df_long <- pivot_longer(df, cols = c(Doseone, Dosetwo), names_to = "Category", values_to = "Value")

# Create a grouped column chart
hchart(df_long, "column", hcaes(x = State, y = Value, group = Category)) %>%
  
  # Set chart title and subtitle
  hc_title(text = "Vaccination Status by State") %>%
  hc_subtitle(text = "Grouped Column Chart") %>%
  
  # Set x-axis and y-axis titles
  hc_xAxis(title = list(text = "State")) %>%
  hc_yAxis(title = list(text = "Vaccination Count")) %>%
  
  # Enable legend
  hc_legend(enabled = TRUE) %>%
  
  # Set colors for the categories
  hc_colors(c("Doseone" = "red", "Dosetwo" = "blue")) %>%
  
  # Enable zooming
  hc_chart(zoomType = "xy") %>%
  
  # Enable exporting functionality
  hc_exporting(
    enabled = TRUE
  ) %>%
  
  # Add credits
  hc_credits(
    enabled = TRUE,
    text = "mygov.in",  # Credits to mygov.in
    href = "https://www.mygov.in/covid-19/"  # Link to mygov.in source
  )




```


### Age(15-18)

```{r}
# Read the dataset
df <- read.csv("indiadata.csv", header = TRUE)

# Convert character columns with commas to numeric
df <- df %>%
  mutate(across(c(Totalcases, Discharged, Deaths, Population, Vaccination,
                  Doseone, Dosetwo, Doseone1518, Dosetwo1518, Doseone1214, Dosetwo1214, Precaution1859, Precaution),
                ~ as.numeric(gsub(",", "", .))))

# Arrange dataframe by descending Vaccination count and select top 20
df <- df %>% 
  arrange(desc(Vaccination)) %>%
  head(20)

# Reshape dataframe from wide to long format
df_long <- pivot_longer(df, cols = c(Doseone1518, Dosetwo1518), names_to = "Category", values_to = "Value")

# Create a grouped column chart
hchart(df_long, "column", hcaes(x = State, y = Value, group = Category)) %>%
  
  # Set chart title and axis titles
  hc_title(text = "Vaccination Status by Age(15-18) in States of India") %>%
  hc_xAxis(title = list(text = "State")) %>%
  hc_yAxis(title = list(text = "Vaccination Count")) %>%
  
  # Enable legend and define colors for each category
  hc_legend(enabled = TRUE) %>%
  hc_colors(c("Doseone1518" = "green", "Dosetwo1518" = "orange")) %>%
  
  # Enable zoom functionality
  hc_chart(zoomType = "xy") %>%
  
  # Enable exporting functionality
  hc_exporting(
    enabled = TRUE
  ) %>%
  
  # Add credits
  hc_credits(
    enabled = TRUE,
    text = "mygov.in",
    href = "https://www.mygov.in/covid-19/"
  )

```


### Age(12-14)

```{r}
# Read the dataset
df <- read.csv("indiadata.csv", header = TRUE)

# Convert character columns with commas to numeric
df <- df %>%
  mutate(across(c(Totalcases, Discharged, Deaths, Population, Vaccination,
                  Doseone, Dosetwo, Doseone1518, Dosetwo1518, Doseone1214, Dosetwo1214, Precaution1859, Precaution),
                ~ as.numeric(gsub(",", "", .))))

# Arrange dataframe by descending Vaccination count and select top 20
df <- df %>% 
  arrange(desc(Vaccination)) %>%
  head(20)

# Reshape dataframe from wide to long format
df_long <- pivot_longer(df, cols = c(Doseone1214, Dosetwo1214), names_to = "Category", values_to = "Value")

# Create a grouped column chart
hchart(df_long, "column", hcaes(x = State, y = Value, group = Category)) %>%
  
  # Set chart title and axis titles
  hc_title(text = "Vaccination Status by Age(12-14) in States of India") %>%
  hc_xAxis(title = list(text = "State")) %>%
  hc_yAxis(title = list(text = "Vaccination Count")) %>%
  
  # Enable legend and define colors for each category
  hc_legend(enabled = TRUE) %>%
  hc_colors(c("Doseone1214" = "purple", "Dosetwo1214" = "brown")) %>%
  
  # Enable zoom functionality
  hc_chart(zoomType = "xy") %>%
  
  # Enable exporting functionality
  hc_exporting(
    enabled = TRUE
  ) %>%
  
  # Add credits
  hc_credits(
    enabled = TRUE,
    text = "mygov.in",
    href = "https://www.mygov.in/covid-19/"
  )

```




Comparitive Analysis (Ind/Usa)
===============================================


##Column {data-width=200}
------------------------------------------------------------------------

### INDIA Vs USA


```{r}

# Load data from CSV file
df <- read.csv("usd.csv", header = TRUE)

# Convert relevant columns to numeric (remove commas)
df <- df %>%
  mutate(across(c(Cases, Deaths, Vaciinationsadministred, Percentage, Partially, Fully), 
                ~ as.numeric(gsub(",", "", .))))

# Create the bar chart
hchart(df, "bar", hcaes(x = Country, y = Cases)) %>%
  
  # Set chart title and axis titles
  hc_title(text = "Cases") %>%
  hc_xAxis(title = list(text = "Country")) %>%
  hc_yAxis(title = list(text = "People Count")) %>%
  
  # Enable legend and define colors
  hc_legend(enabled = TRUE) %>%
  hc_colors("blue") %>%
  
  # Enable exporting functionality
  hc_exporting(
    enabled = TRUE
  ) %>%
  
  # Add credits
  hc_credits(
    enabled = TRUE,
    text = "JohnHopkins",
    href = "https://coronavirus.jhu.edu/covid-19-daily-video"
  )






```




### 


```{r}
# Load data from CSV file
df <- read.csv("usd.csv", header = TRUE)

# Convert relevant columns to numeric (remove commas)
df <- df %>%
  mutate(across(c(Cases, Deaths, Vaciinationsadministred, Percentage, Partially, Fully), 
                ~ as.numeric(gsub(",", "", .))))

# Create the bar chart
hchart(df, "bar", hcaes(x = Country, y = Deaths)) %>%
  
  # Set chart title and axis titles
  hc_title(text = "Deaths") %>%
  hc_xAxis(title = list(text = "Country")) %>%
  hc_yAxis(title = list(text = "People Count")) %>%
  
  # Enable legend and define colors
  hc_legend(enabled = TRUE) %>%
  hc_colors("red") %>%
  
  # Enable exporting functionality
  hc_exporting(
    enabled = TRUE
  ) %>%
  
  # Add credits
  hc_credits(
    enabled = TRUE,
    text = "JohnHopkins",
    href = "https://coronavirus.jhu.edu/covid-19-daily-video"
  )




```


### 


```{r}


# Load data from CSV file
df <- read.csv("usd.csv", header = TRUE)

# Convert relevant columns to numeric (remove commas)
df <- df %>%
  mutate(across(c(Cases, Deaths, Vaciinationsadministred, Percentage, Partially, Fully), 
                ~ as.numeric(gsub(",", "", .))))

# Create the bar chart
hchart(df, "bar", hcaes(x = Country, y = Vaciinationsadministred)) %>%
  
  # Set chart title and axis titles
  hc_title(text = "Vaccines") %>%
  hc_xAxis(title = list(text = "Country")) %>%
  hc_yAxis(title = list(text = "Vaccines Administered")) %>%
  
  # Enable legend and define colors
  hc_legend(enabled = TRUE) %>%
  hc_colors("darkgreen") %>%
  
  # Enable exporting functionality
  hc_exporting(
    enabled = TRUE
  ) %>%
  
  # Add credits
  hc_credits(
    enabled = TRUE,
    text = "CDC",
    href = "https://covid.cdc.gov/covid-data-tracker/#vaccinations_vacc-people-booster-percent-pop5"
  )







```



##Column {.tabset .tabset-fade data-width=450}
------------------------------------------------------------------------

### Daily Cases

```{r}
# Read the dataset
df <- read.csv("who.csv", header = TRUE)

# Convert the 'Date' column to Date format
df$Date <- as.Date(df$Date, format = "%d/%m/%Y")

# Create the highchart object
highchart() %>%
  hc_chart(type = "line") %>%
  
  # Set chart title and axis titles
  hc_title(text = "Comparision of Daily Cases of India & USA") %>%
  hc_xAxis(categories = df$Date) %>%
  hc_yAxis(title = list(text = "Cases")) %>%
  
  # Add series for USA and India
  hc_series(list(name = "Usa", data = df$New_cases_usa),
            list(name = "India", data = df$New_cases_ind)) %>%
  
  # Enable exporting functionality
  hc_exporting(
    enabled = TRUE
  ) %>%
  
  # Enable zooming
  hc_chart(zoomType = "xy") %>%
  
  # Add credits
  hc_credits(
    enabled = TRUE,
    text = "WHO",
    href = "https://data.who.int/dashboards/covid19/cases?m49=356&n=c"
  )


```


### Cumalative Cases

```{r}
# Read the dataset
df <- read.csv("who.csv", header = TRUE)

# Convert the 'Date' column to Date format
df$Date <- as.Date(df$Date, format = "%d/%m/%Y")

# Create the highchart object
highchart() %>%
  hc_chart(type = "line") %>%
  
  # Set chart title and axis titles
  hc_title(text = "Cumulative Cases Over Time") %>%
  hc_xAxis(categories = df$Date) %>%
  hc_yAxis(title = list(text = "Cumulative Cases")) %>%
  
  # Add series for India and USA
  hc_series(list(name = "India", data = df$Cumulative_cases),
            list(name = "USA", data = df$Cumulative_cases_usa)) %>%
  
  # Enable exporting functionality
  hc_exporting(
    enabled = TRUE
  ) %>%
  
  # Add credits
  hc_credits(
    enabled = TRUE,
    text = "WHO",
    href = "https://data.who.int/dashboards/covid19/cases?m49=356&n=c"
  )



```

### Cumalative Deaths

```{r}
# Read the dataset
df <- read.csv("who.csv", header = TRUE)

# Convert the 'Date' column to Date format
df$Date <- as.Date(df$Date, format = "%d/%m/%Y")

# Create the highchart object
highchart() %>%
  hc_chart(type = "line") %>%
  
  # Set chart title and axis titles
  hc_title(text = "Cumulative Deaths Over Time") %>%
  hc_xAxis(categories = df$Date) %>%
  hc_yAxis(title = list(text = "Cumulative Cases")) %>%
  
  # Add series for India and USA
  hc_series(list(name = "India", data = df$Cumulative_deaths),
            list(name = "USA", data = df$Cumulative_deaths_usa)) %>%
  
  # Enable exporting functionality
  hc_exporting(
    enabled = TRUE
  ) %>%
  
  # Add credits
  hc_credits(
    enabled = TRUE,
    text = "WHO",
    href = "https://data.who.int/dashboards/covid19/cases?m49=356&n=c"
  )

```







##Column {.tabset .tabset-fade data-width=350}
------------------------------------------------------------------------

### Case Analysis

```{r}

# Load data from CSV files
df <- read.csv("indiadata.csv", header = TRUE)
d1 <- read.csv("usadata.csv", header = TRUE)

# Convert relevant columns to numeric (remove commas)
df <- df %>%
  mutate(across(c(Totalcases), ~ as.numeric(gsub(",", "", .)))) %>%
  arrange(desc(Totalcases)) %>%
  head(20)

d1 <- d1 %>%
  mutate(across(c(Cases), ~ as.numeric(gsub(",", "", .)))) %>%
  arrange(desc(Cases)) %>%
  head(20)

# Concatenate state names for x-axis labels
concatenated_states <- paste(df$State, d1$State, sep = ", ")

# Scale down the case counts for better visualization
df$cases_scaled <- round(df$Totalcases / 100000)
d1$cases_scaled <- round(d1$Cases / 100000)

# Create stacked column chart
highchart() %>%
  hc_chart(type = "column") %>%
  hc_title(text = "Comparison of Cases by State") %>%
  hc_subtitle(text = "in India and USA") %>%
  hc_xAxis(categories = concatenated_states) %>%
  hc_yAxis(title = list(text = "Case Count (per 100,000)")) %>%
  hc_plotOptions(column = list(
    stacking = "normal"  # Stack bars
  )) %>%
  hc_add_series(name = "India", data = df$cases_scaled) %>%
  hc_add_series(name = "USA", data = d1$cases_scaled) %>%
  hc_chart(zoomType = "xy") %>%
  hc_exporting(
    enabled = TRUE  # Enable exporting functionality
  ) %>%
  hc_credits(
    enabled = TRUE,
    text = "usafacts",
    href = "https://usafacts.org/visualizations/coronavirus-covid-19-spread-map/")

  
```

### Vaccination Analysis

```{r}
library(highcharter)
# Load data from CSV files
df <- read.csv("indiadata.csv", header = TRUE)
d1 <- read.csv("usadata.csv", header = TRUE)

# Convert relevant columns to numeric (remove commas)
df <- df %>%
  mutate(across(c(Vaccination), ~ as.numeric(gsub(",", "", .)))) %>%
  arrange(desc(Vaccination)) %>%
  head(20)

d1 <- d1 %>%
  mutate(across(c(Vaccination), ~ as.numeric(gsub(",", "", .)))) %>%
  arrange(desc(Vaccination)) %>%
  head(20)

# Concatenate state names
concatenated_states <- paste(df$State, d1$State, sep = ", ")

# Scale values to per 100,000
df$Vaccination_scaled <- round(df$Vaccination / 100000)
d1$Vaccination_scaled <- round(d1$Vaccination / 100000)

# Create stacked column chart
highchart() %>%
  hc_chart(type = "column") %>%
  hc_title(text = "Comparison of Vaccination by State") %>%
  hc_subtitle(text = "in India and USA") %>%
  hc_xAxis(categories = concatenated_states) %>%
  hc_yAxis(title = list(text = "Vaccination Count (per 100,000)")) %>%
  hc_plotOptions(column = list(
    stacking = "normal"  # Stack bars
  )) %>%
  hc_add_series(name = "India", data = df$Vaccination_scaled) %>%
  hc_add_series(name = "USA", data = d1$Vaccination_scaled) %>%
  hc_exporting(
    enabled = TRUE  # Enable exporting functionality
  ) %>%
  hc_chart(zoomType = "xy") %>%
  hc_credits(
    enabled = TRUE,
    text = "ourworldindata",
    href = "https://ourworldindata.org/explorers/us-covid-data-explorer?tab=table&facet=none&country=USA~California~Florida~Illinois~Pennsylvania~GEO~North+Carolina~Ohio~New+York+State~Texas~Virginia~Washington~New+Jersey~Arizona~Michigan&pickerSort=desc&pickerMetric=total_vaccinations_per_hundred&hideControls=false&Metric=People+fully+vaccinated&Interval=Cumulative&Relative+to+Population=true"
  )



```


### Probablity Analysis

```{r}
# Load data from CSV files
df <- read.csv("indiadata.csv", header = TRUE)

# Convert relevant columns to numeric (remove commas) and calculate cases per capita
df <- df %>%
  mutate(across(c(Totalcases, Discharged, Deaths, Population, Vaccination),
                ~ as.numeric(gsub(",", "", .))),
         Cases_Per_Capita = round(Totalcases / Population, 2)
  )

# Read data for USA
d1 <- read.csv("usadata.csv", header = TRUE)

# Convert relevant columns to numeric (remove commas) and calculate cases per capita
d1 <- d1 %>%
  mutate(across(c(Cases, Populationestimate), ~ as.numeric(gsub(",", "", .))),
         Cases_Per_Capita = round(Cases / Populationestimate, 2)) %>%
  arrange(desc(Cases_Per_Capita)) %>%
  head(20)

# Concatenate state names
concatenated_states <- paste(df$State, d1$State, sep = ", ")

# Create stacked column chart
highchart() %>%
  hc_chart(type = "column") %>%
  hc_title(text = "Probability Analysis of States Affected in India and USA") %>%
  hc_xAxis(categories = concatenated_states) %>%
  hc_yAxis(title = list(text = "Probability")) %>%
  hc_plotOptions(column = list(
    stacking = "normal"  # Stack bars
  )) %>%
  hc_add_series(name = "India", data = df$Cases_Per_Capita) %>%
  hc_add_series(name = "USA", data = d1$Cases_Per_Capita) %>%
  hc_exporting(
    enabled = TRUE  # Enable exporting functionality
  ) %>%
  hc_chart(zoomType = "xy") %>%
  hc_credits(
    enabled = TRUE,
    text = "ourworldindata",
    href = "https://ourworldindata.org/explorers/us-covid-data-explorer?tab=table&facet=none&country=USA~California~Florida~Illinois~Pennsylvania~GEO~North+Carolina~Ohio~New+York+State~Texas~Virginia~Washington~New+Jersey~Arizona~Michigan&pickerSort=desc&pickerMetric=total_vaccinations_per_hundred&hideControls=false&Metric=People+fully+vaccinated&Interval=Cumulative&Relative+to+Population=true"
  )




```






Map Analysis
=====================================================

Column{.tabset .tabset-fade data-width=500}
--------------------------------------------------------------

### Covid-19 Cases(India) 

```{r}

mapdata <- get_data_from_map(download_map_data("https://code.highcharts.com/mapdata/countries/in/custom/in-all-andaman-and-nicobar.js"))

State <- c("AN", "AP", "AR", "AS", "BR", "CH", "CT", "DA", "DL", "DN", 
           "GA", "GU", "HP", "HR", "JH", "JK", "KA", "KL", "LD", "MH", 
           "ML", "MN", "MP", "MZ", "NL", "NU", "OR", "PB", "PY", "RJ", 
           "SK", "TN", "TR", "UP", "UT", "WB")

# Create the Totalcases vector

Totalcases <- c(10766, 3185164,67049 , 746165, 855267, 100699
                 ,1187697 ,11592,2041112,11592, 263375, 1291459 
                 ,322943,1078968,443831,482039,4088910 
                 ,6907579 ,11415 ,8171926 ,96990,140034 
                 ,1056554  ,239562  ,36033,29625 ,1348440  ,177551  ,793670 
                 ,1326467  ,44932  ,3610743  
                 ,108495 ,2145501  ,452588 ,2126540)

deaths <- c(129, 18844, 296, 8035, 12314, 1185, 14190, 2, 26666,2, 4014, 
            11080, 4245, 10779,5334,4792, 40359, 72043,52,148563, 
            1628,2149,10786 , 734, 782,231, 9215, 20569, 1981,
            9736, 501, 38081, 942, 23713, 7768, 21555)

# Create the data frame
State_pop <- data.frame(State = State, Totalcases = Totalcases,Deaths=deaths)

# Assuming State_pop is your data frame






map_chart <- hcmap("https://code.highcharts.com/mapdata/countries/in/custom/in-all-andaman-and-nicobar.js", 
                   # Assuming this URL is correct for the map data of India
                   data = State_pop,  # Your State population data
                   value = "Totalcases",# Column containing the total COVID cases
                   joinBy = c("hc-a2", "State"),  # Join data by state code and state name
                   name = "Covid Cases",  # Name for the series
                   dataLabels = list(enabled = TRUE, format = '{point.name}'),
                   borderColor = "#FAFAFA",  # Border color for the map
                   borderWidth = 0.1,  # Border width for the map
                   tooltip = list(valueDecimals = 0))  # Tooltip settings

hc_mapNavigation(map_chart, enabled = TRUE)



```





### Covid-19 Deaths(India) 

```{r}

mapdata <- get_data_from_map(download_map_data("https://code.highcharts.com/mapdata/countries/in/custom/in-all-andaman-and-nicobar.js"))

State <- c("AN", "AP", "AR", "AS", "BR", "CH", "CT", "DA", "DL", "DN", 
           "GA", "GU", "HP", "HR", "JH", "JK", "KA", "KL", "LD", "MH", 
           "ML", "MN", "MP", "MZ", "NL", "NU", "OR", "PB", "PY", "RJ", 
           "SK", "TN", "TR", "UP", "UT", "WB")

# Create the Totalcases vector

Totalcases <- c(10766, 3185164,67049 , 746165, 855267, 100699
                 ,1187697 ,11592,2041112,11592, 263375, 1291459 
                 ,322943,1078968,443831,482039,4088910 
                 ,6907579 ,11415 ,8171926 ,96990,140034 
                 ,1056554  ,239562  ,36033,29625 ,1348440  ,177551  ,793670 
                 ,1326467  ,44932  ,3610743  
                 ,108495 ,2145501  ,452588 ,2126540)

deaths <- c(129, 18844, 296, 8035, 12314, 1185, 14190, 2, 26666,2, 4014, 
            11080, 4245, 10779,5334,4792, 40359, 72043,52,148563, 
            1628,2149,10786 , 734, 782,231, 9215, 20569, 1981,
            9736, 501, 38081, 942, 23713, 7768, 21555)

# Create the data frame
State_pop <- data.frame(State = State, Totalcases = Totalcases,Deaths=deaths)

map_chartone <- hcmap("https://code.highcharts.com/mapdata/countries/in/custom/in-all-andaman-and-nicobar.js", 
                      data = State_pop,  
                      value = "Deaths",
                      joinBy = c("hc-a2", "State"),  
                      name = "Covid Deaths", 
                      dataLabels = list(enabled = TRUE, format = '{point.name}'),
                      borderColor = "#FAFAFA",  
                      borderWidth = 0.1,  
                      tooltip = list(valueDecimals = 0)) %>% 
  hc_colorAxis(
    minColor = "#FAFAFA",  # Red color
    maxColor = "#FF0000"   # Red color
  )

hc_mapNavigation(map_chartone, enabled = TRUE)


                    
  
  
```

Column{.tabset .tabset-fade data-width=500}
--------------------------------------------------------------

### Covid-19 Cases(USA)

```{r}

usa <- read.csv("usadata.csv", header = TRUE)

highchart() %>%
  hc_add_series_map(
    usgeojson,
    usa,
    name = "Covid Cases",
    value = "Cases", # Specify the column containing the number of deaths
    dataLabels = list(enabled = TRUE, format = '{point.name}'),
    joinBy = c("woename", "State")
  ) %>%
  hc_mapNavigation(enabled = TRUE)


  

```


### Covid-19 Deaths(USA)

```{r}
usa <- read.csv("usadata.csv", header = TRUE)

highchart() %>%
  hc_add_series_map(
    usgeojson,
    usa,
    name = "Covid Deaths",
    value = "Deaths", # Specify the column containing the number of deaths
    dataLabels = list(enabled = TRUE, format = '{point.name}'),
    joinBy = c("woename", "State")
  ) %>%
  hc_colorAxis(
    minColor = "#FAFAFA",  # Red color
    maxColor = "#FF0000"   # Red color
  ) %>%
  hc_mapNavigation(enabled = TRUE)


```


Datasets
=====================================================

Column{.tabset .tabset-fade}
--------------------------------------------------------------


### Daily Data

```{r}
# Load and display Dataset 1
df1 <- read.csv("who.csv")
datatable(df1)


```


### India Statewise Data

```{r}
# Load and display Dataset 1
df1 <- read.csv("indiadata.csv")
datatable(df1)


```

### Usa Statewise Data

```{r}
# Load and display Dataset 1
df1 <- read.csv("usadata.csv")
datatable(df1)


```

### Usa/India Overview Data

```{r}
# Load and display Dataset 1
df1 <- read.csv("usd.csv")
datatable(df1)


```


